Matching bullets

### 2015-11-17 imaging-paper.Rnw
couple of comments

Rough todo list:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\end{enumerate}

@@

% Methodology
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison. 
3D topographical images are provided on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). 
x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. 
%The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. 
x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

In the Hamby Study, x3p files were created using a NanoFocus lens at 20x magnification. \hh{not sure where this sentences best goes.}

Each fired bullet is provided as a set of six x3p files, where each file is a surface scan between two bullet grooves, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

@@

datadir <- "~/GitHub/x3prproto/images/Hamby252_3DX3P1of2/"

@@

\hh{XXX on a side note - I've got a different relative path to the x3p bullet files ... should we assume a data directory inside the folder? Then we don't have to push the files on a github repo again, but are using the same file structure?}

>>>>

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\end{enumerate}

\hh{I'm putting in footnotes for URLs at the moment, they should probably be included properly in the references.}

@@

% Methodology
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process. These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual.  }

3D topographical images were taken of these bullets using a NanoFocus lens at 20x magnification and made publicly available on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). 
x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. 
%The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. 
x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium\footnote{\url{http://www.openfmc.org/}}), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

Each fired bullet is provided as a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

@@

#datadir <- "~/GitHub/x3prproto/images/Hamby252_3DX3P1of2/"

@@
